\begin{thebibliography}{9}
	\bibitem{computer_vision_alg_apps} 
	Richard Szeliski. 
	\textit{Computer Vision: Algorithms and Applications}. 
	Springer, London, 2010.
	
	\bibitem{pattern_recognition_ml} 
	Christopher M. Bishop. 
	\textit{Pattern Recognition and Machine Learning}. 
	Springer, New York, 2006.
	
	\bibitem{statistical_learning_theory} 
	Vladimir Vapnik. 
	\textit{Statistical Learning Theory}. 
	Wiley, New York, 1998.
	
	\bibitem{dalmohamed_aly}
	Mohamed Aly.
	\textit{Real time Detection of Lane Markers in Urban Streets}.
	1-6, 2008.
		
	\bibitem{dalal_triggs}
	Navneet Dalal and Bill Triggs. 
	\textit{Histograms of Oriented Gradients for Human Detection}.
	1-8, 2005.
	
	\bibitem{tuohy_jones_glavin}
	Shane Tuohy, Edward Jones and Martin Glavin
	\textit{Distance determination for an automobile environment using Inverse Perspective Mapping in OpenCV}.
	1-7, 2010.

	\bibitem{tan_dale_anderson_jonston}
	Sovira Tan, Jason Dale, Andrew Anderson and Alan Johnston.
	\textit{Inverse perspective mapping and optic flow: A calibration method and a quantitative analysis}.
	1-13, 2005.
	
	\bibitem{vapnik_cortes}
	Corinna Cortes and Vladimir Vapnik.
	\textit{Support-Vector Networks}.
	Machine Learning, 20, 273-297:1-25, 1995.
	
	\bibitem{weston_watkins}
	Jason Weston and Simon Watkins.
	\textit{Support Vector Machines for Multi-Class Pattern Recognition}.
	ESANN, 1-6, 1995.
	
	\bibitem{dietterich_bakiri}
	Thomas Dietterich and Ghulum Bakiri.
	\textit{Solving Multiclass Learning Problems via Error-Correcting Output Codes}.
	Journal of Artificial Intelligence Research 2, 263–286:1-24, 1995.
	
	\bibitem{allwein_schapire_singer}
	Erin Allwein, Robert Schapire and Yoram Singer.
	\textit{Reducing multiclass to binary: a unifying approach for margin classifiers}.
	Journal of Machine Learning Research 1, 113–141, 2000.
	
	\bibitem{muad_hussain_samad_mustaffa_majlis}
	Anuar Mikdad Muad, Aini Hussain, Salina Abdul Samad, Mohd. Marzuki Mustaffa, Burhanuddin Yeop Majlis.
	\textit{Implementation of inverse perspective mapping algorithm for the development of an automatic lane tracking system}.
	TENCON 2004. 2004 IEEE Region 10 Conference, 207-210, 2004.
	
	\bibitem{dinamica_accidente_rutiere} 
	Dinamica accidentelor rutiere
	\\\texttt{https://www.politiaromana.ro/ro/structura-politiei-romane/
		unitati-centrale/directia-rutiera/statistici}
	
	\bibitem{database_cars_1}
	Bază de date mașini 1
	\\\texttt{http://www.gti.ssr.upm.es/data/Vehicle\_database.html}
	
	\bibitem{database_cars_2}
	Bază de date mașini 2
	\\\texttt{http://www.robots.ox.ac.uk/~vgg/data3.html}
	
	\bibitem{database_cars_3}
	Bază de date mașini 3
	\\\texttt{http://www.vision.caltech.edu/html-files/archive.html}
	
	\bibitem{database_lanes}
	Bază de date benzi de circulație
	\\\texttt{http://www.mohamedaly.info/datasets/caltech-lanes}
	
	\bibitem{accidente_reduse}
	Self-Driving Cars Could Save 300,000 Lives Per Decade in America
	\\\texttt{https://www.theatlantic.com/technology/archive/2015/09/
		self-driving-cars-could-save-300000-lives-per-decade-in-america/407956/
		?utm\_source=SFTwitter}
	
	\bibitem{tesla_system}
	Tesla Autopilot System
	\\\texttt{https://www.tesla.com/en\_GB/autopilot}
	
	\bibitem{tesla_system}
	Waymo System
	\\\texttt{https://waymo.com/}
	
	
\end{thebibliography}